### 2020-01-20 cv_models.tex
minor update

>>>>

We can understand the Correlation Flow by considering the differences between the VGG, ResNet, and DenseNet architectures,
and, in particular, the number of residual connections.  VGG, while a good model, had been limited by needing the massive
FC layers at the end of the model,requiring significant memory and computational resources.  ResNet greatly improved
on VGG by introducing residual connections, allowing for greater accurary with far fewer parameters.
Indeed, ResNet models of upto 1000 layers have been trained. And we see this in the Corraltion Flow.
We conjuecture that the effeciency and effectivness of ResNet is reflected in the smaller and stable
$\alpha\sim 2.0$,  indicating that the inner layers are very well correlated, really optimized.
In contrast, the DenseNet model contains a massive number of connections and between every layer.
Here, we suppose that DenseNet has too many connections, diluting the Correlation Flow, leaving
many layers very poorly correlated, with large $\alpha$, meaning they are probably not even Heavy Tailed.
